Jilbert's Distinction Centrality

### 2025-03-27 index.qmd
do it

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source("distinction.R")
```

@@

   tab.cent <- function(x, d = 3) { #table function
   library(kableExtra)
   t <- kbl(x, 
       digits = d, row.names = FALSE,
       col.names = c("Node", "Distinction", "Status", "Constraint")) %>% 
      kable_styling(bootstrap_options = c("hover", "condensed", "responsive"))
   return(t)
   }
```

@@

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(here)
   source("distinction.R")
```

@@

   tab.cent <- function(x, d = 3, name = "name") { #table function
   library(kableExtra)
   t <- kbl(x, 
       digits = d, row.names = FALSE,
       col.names = c("Node", "Distinction", "SDistinction", "Status", "Constraint", "Scalar")) %>% 
      kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) 
   save_kable(file = paste(name, ".pdf", sep = ""))
   }
```

@@

```{r}
   medici1 <- as.matrix(read.csv(here("MediciEdgeList.csv")))
   medici1 <- graph_from_edgelist(medici1, directed = FALSE)
   medici2 <- as.matrix(read.csv(here("MediciEdgeListMarriageCut.csv")))
   medici2 <- graph_from_edgelist(medici2, directed = FALSE)
   nomedici <- as.matrix(read.csv(here("NoMediciEdgeList.csv")))
   nomedici <- graph_from_edgelist(nomedici, directed = FALSE)
   distinction(medici1)
   distinction(medici2)
   distinction(nomedici)
   tab.cent(distinction(medici1))
```
